---
layout: interactive
title: Performance Projection - Kris Bryant
author: Michael Lee
github: {user: mdlee12, repo: bryant-projection, branch: "master"}
framework: bootstrap
highlighter: prettify
hitheme: twitter-bootstrap
image:
  feature: bryant2.jpg
  teaser: bryant2.jpg
  related: bryant2.jpg
---

A dynamic rCharts visualization displaying performance projections for Kris Bryant based on his 10 most similar career MiLB comparable players. Read more at <http://middlee.com/milb-similarity-scores/>.

You can change the y-axis parameters by selecting the performance measure you'd like to visualize. Additionally, hover over the points to see player details, and select players in the legend to show or remove their data from the graph.


```{r, echo=F, warning= F, message=F}
# make this an external chunk that can be included in any file
library(rCharts)
library(knitr)
options(width = 100)
opts_chunk$set(message = F, error = F, warning = F, comment = NA, fig.align = 'center', tidy = F, fig.path = "/home/michael/mdlee12.github.com/mdlee12.github.com/_posts/")
options(xtable.type = 'html')
knit_hooks$set(inline = function(x) {
  if(is.numeric(x)) {
    round(x, getOption('digits'))
  } else {
    paste(as.character(x), collapse = ', ')
  }
})
knit_hooks$set(plot = knitr:::hook_plot_html)
```

```{r, rChart, echo=FALSE,results='asis',comment=NA}
bry_age=read.csv("/home/michael/mdlee12.github.com/mdlee12.github.com/bry_age.csv")
bryant=nPlot(HR~Age, data=bry_age, type="lineChart",group="Name")
bryant$addControls("y", value = "HR", values = names(bry_age[, 8:24]))
bryant$yAxis( axisLabel = "Total", width = 50 )
bryant$xAxis( axisLabel = "Age", width = 50 )
bryant$save('bryant.html', cdn = TRUE)
cat('<iframe src="bryant.html" width=100%, height=550></iframe>')
```


Be sure to bookmark my site to check out future visualizations!
